Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Update todo
Reorder scientific study

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels)
% TODO: Scientific study, show how my work integrates in the 3D city reconstruction process.
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.

@@

We may also chose what LOD class(es) to use depending on data availablity and application.
With the current means of data aquisition being limited to building footprints, using OSM data we can only produce CityGML 2.0 LOD-B-models, that is building blocks with simplifed roof shapes (LOD-A being a rendering of the building footprint itself, or building blocks extruded from the footprint to give the building height). \textbf{(Biljecki, Ledoux and Stoter, 2016)}
If we wish to aqquire building assets at a LOD-C level of detail, including features such as doors, windows, alcoves, building decor, indoor features or vegetation, we would have to complete the data with other sources, or rely on procedural methods to populate.
Such procedural techniques have long been available.
\textbf{(Mũller et al, 2006)} present how to accomplish this using shape grammar, a method for describing the possible relations between 
For simple presentation in e.g. animation and videogames or even urban planning software, this could very well be enough.
As long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.

>>>>

% Scietific study
% TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels, road rendering)
% TODO: Scientific study, disposition
    % TODO: Scientific study: Potential application: A method of generating cities on the cheap
% TODO: Scientific study: A set of recommendations.

@@

Another crucial concept in city modelling is the Level Of Detail (LOD). LOD is a definition of a series of different 3D representation of the same data, at different detail levels.
The LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
LOD-A models are renderings of the building footprint itself, or building blocks that have been extruded from the footprint to give the building height.
LOD-B models are building blocks with simplifed roof shapes, and LOD-C models include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\textbf{(Biljecki, Ledoux and Stoter, 2016)}
We may also chose what LOD class(es) to use depending on data availablity and application.
With the current means of data aquisition being limited to building footprints, using OSM data we can only produce CityGML 
If we wish to aqquire building assets at a LOD-C level, we would have to complete the data with other sources, or rely on procedural methods to populate.
Such procedural techniques have long been available.
\textbf{(Mũller et al, 2006)} present how to accomplish this using shape grammar, a method for describing the possible relations between 
For simple presentation in e.g. animation and videogames or even urban planning software, this could very well be enough.
As long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.
